High-Dimensional Regularized Discriminant Analysis

### 2013-04-23 reports/paper-rda.Rnw
Added a section entitled Supplementary Material
Updated paper's title at DMY's recommendation. Also, manually added biometrika bibstyle file.

%% Here are the title, author names and addresses
\title{Another Look at Regularized Discriminant Analysis for High-Dimensional Classification}

@@

each of the $N$ observations to estimate $\Sigma_k$. Hence, for $0 < \lambda

@@

%\bibliographystyle{plainnat}
\bibliographystyle{biometrika}
\bibliography{rda}

>>>>

%% Here are the title, author names and addresses
\title{High-Dimensional Regularized Discriminant Analysis}

@@

each of the $N$ observations in estimating $\Sigma_k$. Hence, for $0 < \lambda

@@

\section*{Supplementary material}
\label{SM}
Supplementary material available at \Bka\ online includes the graphical summary
of the optimal estimates of our classifier from the classification study.

\bibliographystyle{biometrika}
\bibliography{rda}
